Meta-analysis

### 2019-11-13 05_MetaAnalysis.Rmd
Mods in or out? hmmm
clean up imputing code

m5 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + (factor(spray_management) | trial_ref), data = slim_PM_dat) # Model failed to converge

@@

```{r}
library(metafor)

slimer_PM_dat <- slimer_PM_dat[!is.na(slimer_PM_dat$yield_error),]
slimer_PM_dat$yi <- log(slimer_PM_dat$grain_yield.t.ha*1000)
slimer_PM_dat$spray_management

PM_mv_AI <- rma.mv(yi,yield_error,
                   mods = spray_management,
                   method = "ML",
                   random = list(~ spray_management | trial_ref),
                   struct = "UN",
                   data = slimer_PM_dat)

PM_mv_AI

anova(PM_mv_AI, L = rbind(c(0,1,-1,0,0), 
                          c(0,0,-1,1,0),
                          c(0,0,-1,0,1),
                          c(0,0,0,-1,1)))

@@

>>>>

m5 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + (factor(spray_management) | trial_ref), data = slim_PM_dat)

@@

We need to impute the variances which are missing for a few of the trials. These trials `r paste(unique(slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),c("location","year", "trial_ref")])` were analysed and reported that there was no significant difference between the treatments in each trial. So therefore we need the imputed variances not to show a significant difference.

There are `r sum(is.na(slimmer_PM_dat$yield_error))` treatments without yield error in our data, and `r sum(!is.na(slimmer_PM_dat$yield_error))` where yield error was recorded.

Plotting a histogram of the variances show that the yield is not normally distributed. A log transformation, however, shows a normal disrtubution. We can use the mean and standard deviation of the log(V) to sample variances for the treatments where V is mission.

We will evaluate wheather the imputed variances confer a significant difference to the recorded means. I created a distance matrix of two standard errors above the mean against two standard errors below the mean. If any errors don't overlap, infering signicifant difference, the imputed variances are discarded and resampled until all treatment variances show no significant differences.

```{r imputing_variances}

hist(slimmer_PM_dat$yield_error) # yield error is not normally distributed
hist(log(slimmer_PM_dat$yield_error)) # a log transformation shows it is normally distributed

# generate yield error values
for(i in 0:500){

   # Imputing missing log variances
   log_Yerror <- rnorm(n = sum(is.na(slimmer_PM_dat$yield_error)),
               mean = mean(log(slimmer_PM_dat$yield_error), na.rm = TRUE),
               sd = sd(log(slimmer_PM_dat$yield_error), na.rm = TRUE))

   # First lets convert Variance to standard error for all the variables that have variance recorded
   slimmer_PM_dat$yield_SE <- 
      sqrt(slimmer_PM_dat$yield_error)/sqrt(slimmer_PM_dat$n)

   # Second; adding the imputed standard errors
   slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"] <-
      sqrt(exp(log_Yerror))/sqrt(slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"n"])

# all errorbars should overlap so they are consistant with the meta-data describing no significant difference bettween treatments
# lets test to make sure
if(
   max(outer(X = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] -
               (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
             Y = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] +
               (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
             FUN = "-")
       ) > 0){

   message(paste("\nWarning!!: Imputed yield errors show significant differences when they should not, rerun chunk", "i =",i))
   next()
   }else{
      message(paste(i,"iterations: ", "imputed variances now show no significant distances :)\n Now adding variances to data "))

      # Plot the imputed errors for each trial
      Vplot <- slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),] %>%
         ggplot(aes(y = grain_yield.t.ha, trial))+
         #geom_point()+
         geom_pointrange(ymin = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] -
                            (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
                         ymax = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"grain_yield.t.ha"] +
                            (2*slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error),"yield_SE"]),
                         position = "jitter"
                         )+
         ylim(0.2,1.5)

      slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_error"] <- exp(log_Yerror)
      print(Vplot)
      break()}
}

@@

```{r meta_1}
library(metafor)

slimmer_PM_dat$yi <- slimmer_PM_dat$grain_yield.t.ha
slimmer_PM_dat$vi <- slimmer_PM_dat$yield_error

slimmer_PM_dat$spray_management <- factor(slimmer_PM_dat$spray_management)
table(slimmer_PM_dat$spray_management)

PM_mv_AI <- rma.mv(yi,vi,
                   mods = ~ spray_management,
#                   method = "ML",
                   random = list(~ spray_management | trial),
                   struct = "UN",
                   data = slimmer_PM_dat)

summary(PM_mv_AI)

```{r inspect_for_outliers}
head(slimmer_PM_dat)

slimmer_PM_dat %>%
#   filter(spray_management == "Late_plus") %>%
   ggplot(aes(prop_yield_gain, fill = spray_management))+
   geom_histogram(alpha = 0.5)

slimmer_PM_dat %>%
   filter(spray_management == "Late_plus") %>%
   ggplot(aes(prop_yield_gain, fill = trial_ref))+
   geom_histogram(alpha = 0.5)

slimmer_PM_dat %>%
   filter(spray_management == "Recommended") %>%
   ggplot(aes(prop_yield_gain, fill = trial_ref))+
   geom_histogram(alpha = 0.5)
